Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-16 paper.tex
Algo

Note that the difference $F(\gamma) - F(P^\omega_{\Ccal_k}(\gamma))$ may be calculated without knowing $\gamma^*$, as shown by the following lemma.
\begin{lemma}\label{lemma:lyapunov_decrease}
	Take $\gamma$ in $\IR^{mn}_{+*}$. The decrease in value of the Lyapunov function can be calculated with the following formula:
	\begin{equation} \label{eq:kl_diff_scal}
	F(\gamma) - F(P^\omega_{\Ccal_k}(\gamma)) = 
	\scal{\mu^k}{\varphi_\omega \left(\frac{A_k \gamma}{\mu^k}\right)},
	\end{equation}
	where
	\begin{equation}
	\varphi_\omega(x) = x(1-x^{-\omega}) - \omega \log x
	\end{equation}
	is a real function, applied coordinate-wise.
\end{lemma}
\begin{proof}
From \eqref{KL}, we have $F(\gamma^1)-F(\gamma^2)= \sum_{i,j}\left(\gamma^*_{i,j}\log(\gamma^2_{i,j}/\gamma^1_{i,j})+\gamma^1_{i,j}-\gamma^2_{i,j}\right)$. The result can then be deduced from relations \eqref{eq:def_or_proj} and \eqref{scaling}.
\end{proof}
Thus, calculating the decrease in value of the function $F$ is relatively cheap and straightforward. In Figure \ref{phi_omega}, we illustrate the functions  $\varphi_\omega$ for several values of $\omega$.
Notice that for the Sinkhorn algorithm, which corresponds to $\omega=1$, the function $\varphi_\omega$ is always nonnegative. For other values $1\le\omega<2$, it is nonnegative for arguments close to 1.
\begin{figure}[ht!]
\begin{center}
\includegraphics[width=11cm]{phi_omega.png}
\caption{\label{phi_omega} Plot of functions $\varphi_\omega(x)$ for different values $1\leq \omega\leq 2$ and   $x\in[10^{-2}, 10^1]$.}
\end{center}
\end{figure}
\subsection{Proposed algorithm}

>>>>

Note that the difference $F(\gamma) - F(P^\omega_{\Ccal_k}(\gamma))$ may be calculated without knowing $\gamma^*$, as shown by the following lemma.
\begin{lemma}\label{lemma:lyapunov_decrease}
	Take $\gamma$ in $\IR^{mn}_{+*}$. The decrease in value of the Lyapunov function can be calculated with the following formula:
	\begin{equation} \label{eq:kl_diff_scal}
	F(\gamma) - F(P^\omega_{\Ccal_k}(\gamma)) = 
	\scal{\mu^k}{\varphi_\omega \left(\frac{A_k \gamma}{\mu^k}\right)},
	\end{equation}
	where
	\begin{equation}
	\varphi_\omega(x) = x(1-x^{-\omega}) - \omega \log x
	\end{equation}
	is a real function, applied coordinate-wise.
\end{lemma}
\begin{proof}
From \eqref{KL}, we have $F(\gamma^1)-F(\gamma^2)= \sum_{i,j}\left(\gamma^*_{i,j}\log(\gamma^2_{i,j}/\gamma^1_{i,j})+\gamma^1_{i,j}-\gamma^2_{i,j}\right)$. The result can then be deduced from relations \eqref{eq:def_or_proj} and \eqref{scaling}.
\end{proof}
Thus,  the decrease in value of the function $F$ for a over-relaxed projection associated to $\Ccal_k$ is cheap to estimate, since its computational cost is  linear with respect to the dimension of data $\mu^k$. In Figure \ref{phi_omega}, we illustrate the functions  $\varphi_\omega$ for several values of $\omega$.
Notice that for the Sinkhorn algorithm, which corresponds to $\omega=1$, the function $\varphi_\omega$ is always nonnegative. For other values $1\le\omega<2$, it is nonnegative for arguments close to 1.
\begin{figure}[ht!]
\begin{center}
\includegraphics[width=11cm]{phi_omega.png}
\caption{\label{phi_omega} Plot of functions $\varphi_\omega(x)$ for different values $1\leq \omega\leq 2$ and   $x\in[10^{-2}, 10^1]$.}
\end{center}
\end{figure}
\subsection{Proposed algorithm}
